lifespan_eda

### 2024-02-19 eda/lifespan_eda.Rmd
qc by euler number

```{r, eval=FALSE}
gamlss(formula = rh_Vol_posteriorcingulate ~ pb(age_days) + sexMale + pb(sex.age) + site, sigma.formula= ~ pb(age_days) + sexMale + site, data=imagen.df)
```

>>>>

```{r, eval=FALSE}
gamlss(formula = rh_Vol_posteriorcingulate ~ pb(age_days) + sexMale + sex.age + site, sigma.formula= ~ pb(age_days) + sexMale + site, data=imagen.df)
```
